\documentclass{article}

\usepackage[top=0.75in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{enumerate,hyperref,amssymb,caption}

\input{../course-specific-macros.tex}

\begin{document}



\begin{center}
{\bf \large \course{}\\
Graduate Seminar} \\
\end{center}

\vspace{0.25in}


\noindent \begin{tabular}{@{}ll}
\begin{tabular}{ll}
{\bf Course information:}& \course{} -- Graduate Seminar \\
& \semester \\
& Course format: Web-enhanced \\
& \\
{\bf Meeting times:} & W 1:30-2:20 \end{tabular} &
\begin{tabular}{ll}
{\bf Instructor:}& \prof \\
& \profemail \\
& {\tt(251) 219-8163} \\
& \\
{\bf Office hours:} & By appointment
\end{tabular}
\end{tabular}

\section*{\fontsize{12}{15}\selectfont Student Success}
I am committed to helping each and every one of you achieve your goals. I fundamentally believe that \textbf{everyone is a math person} and is capable of succeeding in this course. If there is something we could do differently that will help you succeed, please come talk to me. 

There are many services on campus to help you succeed. I enthusiastically support the mission of our Office of Student Disability Services; if you are registered with them, please come speak to me in office hours so I can ensure I am doing everything needed to enable your success.


\section*{\fontsize{12}{15}\selectfont Basic Needs Security}
Any student who has difficulty affording groceries or accessing sufficient food to eat every day, or who lacks a safe and stable place to live, and believes this may affect their performance in the course, is urged to contact the Dean of Students for support. Furthermore, please notify the professor if you are comfortable in doing so. This will enable me to try and provide information on accessing additional resources.  Information on the campus food pantry is available at \url{https://southalabama.edu/departments/sga/foodpantry.html}.


\section*{\fontsize{12}{15}\selectfont Communication Plan}

\begin{itemize}
\item The best way to reach me is by email at {\tt drewlewis@southalabama.edu}. 
\item Additionally, you can text (preferred) or call me at {\tt(251) 219-8163}. This is my cell phone, not an office number.
\end{itemize}

\section*{\fontsize{12}{15}\selectfont Office Hours and Instructor Availability}

Office hours are times I have specifically set aside to be available for you to drop-in to ask questions, attempt reassessments, or talk with me about anything else. They would probably be better named \textbf{Student Hours}. Because of social distancing requirments, all office hours will be done virtually and by appointment; {\bf send me an email to schedule a time}. The Zoom link for office hours is posted in \LMS.

\section*{\fontsize{12}{15}\selectfont Disaster Plan}
In the event of a campus closure (e.g. due to a pandemic or weather), we will continue to meet virtually via Zoom at our regular time as best we can. In such an event, I ask that we all extend grace and patience to each other; we will all do the best we can in the circumstances.


\section*{\fontsize{12}{15}\selectfont Course Description}
Student Seminar. Topics covered vary. This course may be repeated indefinitely, but only two credits count towards the degree. Grading system: satisfactory/unsatisfactory.


\section*{\fontsize{12}{15}\selectfont Topics}
We will discuss issues relating to to teaching and researching mathematics. At the beginning of the semester, most weeks we will have an assigned reading, to be followed by an asynchronous discussion and/or a discussion during our class meeting. Towards the end of the semester, each student will present on a mathematics paper they have read.


\section*{\fontsize{12}{15}\selectfont Grading}
The course is graded as Satisfactory/Unsatisfactory.



\section*{\fontsize{12}{15}\selectfont Student Academic Conduct Policy}
All students are expected to adhere to the Student Academic Conduct Policy, which you can view at
{\tt http://www.southalabama.edu/bulletin/current/student-affairs/conduct.html}.  Students violating this policy will be given one or more of the following penalties based on the severity of the offense:  1) Loss of all mastery checkmarks on all standards affected by the misconduct; 2) Reduction in final course grade by a letter grade; 3) Automatic course failure.


\section*{\fontsize{12}{15}\selectfont Syllabus Changes}
We may want to make changes to this syllabus due to the development of the pandemic, weather events like hurricanes, etc. Any changes made will reflect the spirit of this original syllabus, and will be updated on \LMS.




\end{document}
